Size-differentiated Export in Different Dynamical Regimes in the Ocean

### 2019-08-28 size_differentiated_export.tex

\documentclass[article,linenumbers]{agujournal2018}
\usepackage{apacite}
\usepackage{url} %this package should fix any errors with URLs in refs.

@@

%FIG6
\begin{figure}[ht!]
	\centering
	\includegraphics[width = .8\linewidth]{figures/Fig6.png}
	\caption{[left] 
	The median depth anomaly of particles with a sinking speed (a) 0.025 m/d, (b) 1 m/d, (c) 5 m/d within each grid cell for the winter case 25 days after particles are released. The `depth anomaly' is with respect to the `expected' sinking depth (= sinking speed $\times$ time since release).  
	%Gridded anomaly in the median depth of particles 25 days after particle release in the Winter experiment, with 
	%sinking speed (a) 0.025 m/d, (b) 1 m/d, (c) 5 m/d. 
	Blue (red) grid cells indicate that the median depth of particles in this cell is deeper (shallower) than expected, based on a 1D gravitational model where $z = w_s\timest$. [right] (d) Probability Distribution Function (PDF) of particles as a function of depth for each velocity class. The winter distribution is shown as thick lines, while the summer distribution is represented by the shaded regions. Triangle markers indicate the expected depth of particles after 25 days based on the 1D gravitational model, which is used as a reference to compute the depth anomalies. Release depth is indicated by the thick dashed line.}	
	\label{fig: particle_depth_distribution}
\end{figure}

>>>>

\documentclass[article,linenumbers]{agujournal2018}
\usepackage{apacite}
\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{amsmath}

@@

%FIG6
\begin{figure}[ht!]
	\centering
	\includegraphics[width = .8\linewidth]{figures/Fig6.png}
	\caption{[left] 
	The median depth anomaly of particles with a sinking speed (a) 0.025 m/d, (b) 1 m/d, (c) 5 m/d within each grid cell for the winter case 25 days after particles are released. The `depth anomaly' is with respect to the `expected' sinking depth (= sinking speed $\times$ time since release). Blue (red) grid cells indicate that the median depth of particles in this cell is deeper (shallower) than expected, based on a 1D gravitational model where $z = w_s\times t$. [right] (d) Probability Distribution Function (PDF) of particles as a function of depth for each velocity class. The winter distribution is shown as thick lines, while the summer distribution is represented by the shaded regions. Triangle markers indicate the expected depth of particles after 25 days based on the 1D gravitational model, which is used as a reference to compute the depth anomalies. Release depth is indicated by the thick dashed line.}	
	\label{fig: particle_depth_distribution}
\end{figure}
